Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-16 research_class/paper.tex
Change "at time of paper" tense to present.
Not sure, but I prefer this.
I would remove this sentence.
It seems redundant in a short paragraph, but it *is* nice to start the paragraph
with a direct comment. Not sure about this one.

The signaling transport itself is not defined as part of WebRTC.
This is up to the application designer. The JavaScript interface used
for establishing the initial connection (signaling) in the WebRTC 1.0
standard is somewhat complicated. A competing standard called Object
Real-time Communication (ORTC) is working to define a simpler and more
modular JavaScript API for WebRTC signaling \cite{ortc2014}. However,
at the time of this paper, the ORTC interface was not yet widely
supported and still in a state of flux. The use of PeerJS provides an
abstraction that is likely to transparently support ORTC in the future.

@@

The PeerJS client library provides an simple abstraction over the
native browser WebRTC APIs. The WebRTC API standards are not yet
finalized and so different browsers and browser releases may support
different versions of the WebRTC draft APIs. %TODO/CITE
The PeerJS client library abstracts over these differences and
provides a common interface so that the application developer does not
have to deal directly with browser differences.

>>>>

The signaling transport itself is not defined as part of WebRTC.
This is up to the application designer. The JavaScript interface used
for establishing the initial connection (signaling) in the WebRTC 1.0
standard is somewhat complicated. A competing standard called Object
Real-time Communication (ORTC) is working to define a simpler and more
modular JavaScript API for WebRTC signaling \cite{ortc2014}. However,
at the time of this paper, the ORTC interface is not yet widely
supported and is still in a state of flux. The use of PeerJS provides an
abstraction that is likely to transparently support ORTC in the future.

@@

The WebRTC API standards are not yet
finalized and so different browsers and browser releases may support
different versions of the WebRTC draft APIs. %TODO/CITE
The PeerJS client library abstracts over these differences and
provides a common interface so that the application developer does not
have to deal directly with browser differences.
